Columnar VCF for Biobank scale datasets using Zarr

### 2024-04-15 paper.tex
Some Zarr bio refs
Closes #7
Closes #23

>>>>

Zarr has recently been gaining traction in biological applications
also. EUGENe~\citep{klie2023predictive} is a toolkit for 
for applying deep-learning methods to genomic sequence data,
integrating with PyTorch [citation?].

Spatial Omics:
emObject~\citep{baker2023emobject}
SpatialData~\citep{marconato2024spatialdata}
